Online Social Cohesion Reflects Real-World Group Action in Syria during the Arab Spring

### 2020-06-01 manuscript.Rmd
Edits to results

For social cohesion and count of all events, there was a consistent period 
of above-chance RR from the 7th-12th and 36th-47th window 
(Figure \@ref(fig:plot-wcrqa-targ-all)). DET was largely above chance 
from the 46th to the 61st window (Figure \@ref(fig:plot-wcrqa-targ-all)).

@@

For social cohesion and count of all events, there was a consistent period of
above- or nearly above-chance DET from the 7th-13th and 26th-47th 
windows (Figure \@ref(fig:plot-wcrqa-source-targ-all)). DET also 
showed above- or nearly above-chance values in windows 7th-17th and 
intermittent peaks between the 34th and 61st windows (Figure 
\@ref(fig:plot-wcrqa-source-targ-all)).

>>>>

For social cohesion and count of all events, there was a consistent period 
of above-chance RR from the 7th-12th and 36th-47th window. DET was largely 
above chance from the 46th to the 61st window 
(Figure \@ref(fig:plot-wcrqa-targ-all)).

@@

For social cohesion and count of all events, there was a consistent period of
above- or nearly above-chance DET from the 7th-13th and 26th-47th 
windows. DET also showed above- or nearly above-chance values in windows 7 
through 17 and intermittent peaks between the 34th and 61st windows 
(Figure \@ref(fig:plot-wcrqa-source-targ-all)).

### 2020-06-01 manuscript.tex
Edits to results

For social cohesion and count of all events, there was a consistent period
of above-chance RR from the 7th-12th and 36th-47th window
(Figure \ref{fig:plot-wcrqa-targ-all}). DET was largely above chance
from the 46th to the 61st window (Figure \ref{fig:plot-wcrqa-targ-all}).

@@

For social cohesion and count of all events, there was a consistent period of
above- or nearly above-chance DET from the 7th-13th and 26th-47th
windows (Figure \ref{fig:plot-wcrqa-source-targ-all}). DET also
showed above- or nearly above-chance values in windows 7th-17th and
intermittent peaks between the 34th and 61st windows (Figure
\ref{fig:plot-wcrqa-source-targ-all}).

>>>>

For social cohesion and count of all events, there was a consistent period
of above-chance RR from the 7th-12th and 36th-47th window. DET was largely
above chance from the 46th to the 61st window
(Figure \ref{fig:plot-wcrqa-targ-all}).

@@

For social cohesion and count of all events, there was a consistent period of
above- or nearly above-chance DET from the 7th-13th and 26th-47th
windows. DET also showed above- or nearly above-chance values in windows 7
through 17 and intermittent peaks between the 34th and 61st windows
(Figure \ref{fig:plot-wcrqa-source-targ-all}).
